\LARGE \bf Artifical Cognition for Social Human-Robot Interaction:\\ An Implementation

### 2016-06-13 paper.tex
New tentative title
Update affiliations

\title{\LARGE \bf
Human-Robot Interaction: Tackling the AI Challenges
}

\author{Séverin Lemaignan, Mathieu Warnier, E. Akin Sisbot, Rachid Alami}

\address{
CNRS, LAAS, 7 avenue du Colonel Roche, F-31400 Toulouse, France\\
Univ de Toulouse, LAAS, F-31400 Toulouse, France\\
{\tt firstname.lastname@laas.fr}
}

@@

This work has been supported by EU FP7 ``SAPHARI'' under grant agreement no.
ICT-287513.

>>>>

\title{\LARGE \bf
Artifical Cognition for Social Human-Robot Interaction:\\ An Implementation
}

\author{Séverin Lemaignan$^{1,2}$, Mathieu Warnier$^1$, E. Akin Sisbot$^1$,
Rachid Alami$^1$}

\address{
$^1$CNRS, LAAS, 7 avenue du Colonel Roche, F-31400 Toulouse, France\\
Univ de Toulouse, LAAS, Toulouse, France\\
{\tt firstname.surname@laas.fr}
}

\address{
$^2$Centre for Robotics and Neural Systems\\
Plymouth University, Plymouth, United Kingdom\\
{\tt firstname.surname@plymouth.ac.uk}
}

@@

This work has been partially supported by EU FP7 ``SAPHARI'' (grant ICT-287513),
and the EU H2020 Marie Sklodowska-Curie Actions project DoRoThy (grant 657227).
